%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\usepackage{marvosym} % Allows the use of symbols
\usepackage{amsmath} % Allows the use of symbols
\usepackage{enumitem}
%\addbibresource{bibliography.bib}

\begin{document}
\header{natalie}{tay}
{computer engineer}

% In the aside, each new line forces a line break

\begin{aside}
	\section{online}
	\Email~ \href{mailto:nat@lie.sg}{nat@lie.sg}
	%\href{http://blog.wtf.sg}{http://blog.wtf.sg}
	%\href{https://www.facebook.com/natalie.tsw}{fb://natalie.tsw}
	\href{http://github.com/nattsw}{nattsw@github}
	\href{http://sg.linkedin.com/in/natalietsw}{natalietsw@linkedin}
	\section{languages}
	english (proficient)
	mandarin
	\section{programming}
	{\color{red} $\varheartsuit$} Java (Android)
	C\#
	{\color{red} $\varheartsuit$} Ruby
	C
	C++
	Objective-C
	JavaScript
	\section{technical skills}
	HTML \& CSS
	\LaTeX
	Git
	*nix
\end{aside}

\section{about}

\begin{tabular}{ p{0.45cm} p{6.5cm} p{0.45cm} p{6.5cm} }
	\Female 	& Tay Shu Wen, Natalie	 & \Scorpio &  DOB: 16/11/1989\\
	\Letter & 434 Clementi Ave 3, Singapore 120434 & \Mobilefone & (+65) 86123211 \\
\end{tabular}

\section{experience}

\begin{entrylist}
	\entry
	{02 2016 - now  \ \ }
	{Pivotal Labs}
	{Software Engineer}
	{Worked on several projects using TDD and Agile methodologies:
	\begin{itemize}[itemsep=0pt,topsep=0pt]
	\item An Android app for a large carmaker, which targeted API 19 - 23. Implemented fuel, analytics and servicing features, and enablement of client engineers through pairing. Liaised with global team to ensure that the quality and alignment of the app is maintained across regions.
	\item An online Liquor Store in Ruby on Rails using an open source e-commerce solution. It involved integration with commercial warehouse for delivery and store upkeep.
	\end{itemize}}
	
	\entry
	{07 2015 - 02 2016   \ \ }
	{Neo Innovation}
	{Software Engineer}
	{Worked on several projects using TDD and Agile methodologies:
	\begin{itemize}[itemsep=0pt,topsep=0pt]
	\item A worldwide fitness concierge: matches trainees to vetted trainers in Ruby on Rails. The app was live and involved service maintenance, feature expansion, and migration.
	\item An Android concierge application for a large mobile company, which targeted API 18 - 23. It was a system application on a flagship phone, which had to work with a 10MB size limit and other unconventional constraints. The project involved a handover to the overseas team.
	\end{itemize}}

	\entry
	{12 2012 - 06 2015   \ \ }
	{ST Electronics (Info-Comm)}
	{Software Engineer}
	{Defence Electronics Division
	\begin{itemize}[itemsep=0pt,topsep=0pt]
	\item Built a RF matrix using an Atmel AVR UC3 microcontroller
	\item Built a front-end library in C to handle high throughput graphics rendering
	\item Project requirement analysis and solutioning
	\item Liaise with vendors and clients to develop solutions and manage project
	\item Delivered a solution which involved interfacing with several pieces of hardware via serial and wireless interfaces
	\end{itemize}}
	
	\entry
	{06 - 12 2011 }
	%{\href{http://www.np.edu.sg/ict/facilities/rhymes/Pages/loc\_rhymes.aspx}{RHyMeS Center, Ngee Ann Polytechnic}}
	{ST Electronics (Info-Comm)}
	{Assoc Engineer}
	{Defence Electronics Division \\Worked on R\&D project which required:
	\begin{itemize}[itemsep=0pt,topsep=0pt]
	\item Extensive knowledge on Human-Computer Interaction for RF tools
	\item Optimisation of computer memory use
	\item Radio communications protocols
	\item Communicating implementation details and complications to high-level stakeholders
	\end{itemize}}
	
	\entry
	{04 - 08 2009}
	{ST Electronics (Info-Comm)}
	{Software Engineer}
	{Defence Electronics Division \\Was recommended and contracted to work on classified project:
	\begin{itemize}[itemsep=0pt,topsep=0pt]
	\item Search and sort of large data
	\item Categorisation of information
	\item Interfacing with several communications equipment
	\end{itemize}}
\end{entrylist}

\section{education}

\begin{entrylist}
	\entry
	{2009 - 2012}
	{Bachelors of Engineering (BEng)}
	{National University of Singapore}
	{
		Major in Computer Engineering
	}
	\entry
	{2006 - 2009}
	{Diploma in Electronics and Computer Engineering}{Ngee Ann Polytechnic}
	{
		Diploma with Merit\\
	}
	\entry
	{2005}
	{GCE 'O' Levels}{Clementi Town Secondary School}
	{}
\end{entrylist}
\pagebreak
\section{Notable Projects}
\begin{entrylist}
	\entry{2012}
	{Mobile Ground Station for Unmanned Aerial Vehicles}
	{}
	{
		A Ground Control Station built on the iPad (iOS 6) interfacing for a custom UAV. The UAV took part in the DARPA UAVForge competition. Communication was via Wi-Fi and 3G.

	}
	\entry{2012}
	{Social Care Assistance Network}
	{}
	{Social Network for Android (V15, Ice Cream Sandwich) devices, developed for aiding in quick response to non-emergency situations. Involved the usage of an indoor localization server capable of pinpointing indoor location via power signal of network device.}
	\entry{2012}
	{Networked Bomberman}
	{}
	{A multiplayer clone of the classic Bomberman for the browser and Blackberry Playbook made using CraftyJS (JS game engine) and NodeJS. Drew graphics and implemented game logic. }
	\entry{2010}
	{i8051 Sequencer}
	{}
	{Designed the 8051 sequencer which contains the algorithm for implementing assembly instructions of the Intel 8051 in the Industry Standard Architecture. Used the Spartan 3A Evaluation Kit (FPGA) to test the sequencer logic in VHDL.}
	\entry{2009}
	{eSuite}
	{}
	{A web-based control system in C\# to remotely control and monitor the activities of an indoor environment. Sensor boards, logic circuits, and motor drivers were built from scratch. The suite features audio-video transmission, motion detection, temperature sensors, automatic triggers and alarms via SMS or email.}

\end{entrylist}



%\section{Groups}
%
%\begin{entrylist}
%	\entry
%	{2014}
%	{R User Group}
%	{Attendee}
%	{Avid interest in R Language due to its wide usage by statisticians, for data mining and analysis.}
%	
%\end{entrylist}
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%	\nocite{*}
%	\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%	\nocite{*}
%	\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}
\section{Interests}
swimming, information visualisation, inline skating, reading, gaming
\end{document}
